Fixed-Parameter Tractable Sampling for RNA Design with Multiple Target Structures

### 2018-08-30 supplement.tex
Reformat for BMC

\PassOptionsToPackage{utf8}{inputenc}
\documentclass[12pt]{bioinfo}
\copyrightyear{2015} \pubyear{2015}

\access{Advance Access Publication Date: Day Month Year}
\appnotes{Manuscript Category}

@@

\usepackage{booktabs} % for much better looking tables
\usepackage{array} % for better arrays (eg matrices) in maths
% \usepackage{paralist} % very flexible & customisable lists (eg. enumerate/itemize, etc.)
%   \let\itemize\compactitem
%   \let\enditemize\endcompactitem
%   \let\enumerate\compactenum
%   \let\endenumerate\endcompactenum
%   \let\description\compactdesc
%   \let\enddescription\endcompactdesc
%   \pltopsep=1pt
%   \plitemsep=1pt
%   \plparsep=1pt  
\usepackage{hyperref} 
\usepackage{xspace} 
%\usepackage{geometry} 
\usepackage{amsmath,amssymb} 
\usepackage{bm}
\usepackage{verbatim}
\usepackage{longtable}
\usepackage[vlined]{algorithm2e}

@@

%\newtheorem{algorithm}{Algorithm}
\newtheorem{axiom}{Axiom}
\newtheorem{hypothesis}{Working Hypothesis}
\renewenvironment{proof}[1][]{\noindent \em Proof\ifthenelse{\equal{#1}{}}{}{ (#1)}:~}{}

@@

@@

\begin{document}
%\newgeometry{margin=2cm}
\onecolumn

\appendix
{\centering \relsize{+4}\textbf{Supplementary Material}\\[1em] Fixed-Parameter Tractable Sampling\\ for RNA Design with Multiple Target Structures\\%
%{\relsize{-1}\BackupTitle}\\
}
\relsize{+1}

@@

\bibliographystyle{natbib}
%\bibliographystyle{achemnat}
%\bibliographystyle{plainnat}
%\bibliographystyle{abbrv}
%\bibliographystyle{bioinformatics}
%
%\bibliographystyle{plain}
%
\bibliography{biblio}

>>>>

\documentclass[10pt]{article}

@@

\usepackage{booktabs} % for much better looking tables
\usepackage{array} % for better arrays (eg matrices) in maths
% \usepackage{paralist} % very flexible & customisable lists (eg. enumerate/itemize, etc.)
%   \let\itemize\compactitem
%   \let\enditemize\endcompactitem
%   \let\enumerate\compactenum
%   \let\endenumerate\endcompactenum
%   \let\description\compactdesc
%   \let\enddescription\endcompactdesc
%   \pltopsep=1pt
%   \plitemsep=1pt
%   \plparsep=1pt  
\usepackage{hyperref} 
\usepackage{xspace}

\usepackage[margin=1in]{geometry}

\usepackage{amsmath,amssymb} 
\usepackage{bm}
\usepackage{verbatim}
\usepackage{longtable}
\usepackage[vlined]{algorithm2e}

@@

%\newtheorem{algorithm}{Algorithm}
\newtheorem{axiom}{Axiom}
\newtheorem{hypothesis}{Working Hypothesis}
\newenvironment{proof}[1][]{\noindent \em Proof\ifthenelse{\equal{#1}{}}{}{ (#1)}:~}{}

@@

\newcommand{\citep}[1]{\cite{#1}}
\newcommand{\citet}[1]{\cite{#1}}

@@

\begin{document}
\onecolumn

\appendix
{\centering \Large \textbf{Supplementary Material}\\[1em] Fixed-Parameter Tractable Sampling\\ for RNA Design with Multiple Target Structures\\%
}

@@

\bibliographystyle{plain}
%\bibliographystyle{achemnat}
%\bibliographystyle{plainnat}
%\bibliographystyle{abbrv}
%\bibliographystyle{bioinformatics}
%
%\bibliographystyle{plain}
%
\bibliography{biblio}
